\documentclass[a4paper,12pt]{article}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry} 
\usepackage{amsmath,amssymb,amsthm,algorithm,algorithmic,graphicx,yhmath,url,enumitem,lscape,hyperref}
\usepackage{wrapfig,subfigure}
\usepackage{lineno}

\newcounter{problem}
\newcounter{remark}
\newcounter{hint}
\newenvironment{remark}{\refstepcounter{remark} \vspace{0.1cm} \par \noindent {\bf Remark \arabic{remark}}}{\vspace{0.3cm}}
\newenvironment{hint}{\refstepcounter{hint} \vspace{0.1cm} \par \noindent {\bf Hint \arabic{hint}}}{\vspace{0.3cm}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Rn}{\mathbb{R}^n}
\newcommand{\Rnn}{\mathbb{R}^{n \times n}}
\newcommand{\bes}{\begin{equation*}}
\newcommand{\ees}{\end{equation*}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bms}{\begin{multline*}}
\newcommand{\emults}{\end{multline*}}

% Matrices
\newcommand{\bbm}{\begin{bmatrix}}
\newcommand{\ebm}{\end{bmatrix}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}

% Strecthing
\renewcommand{\arraystretch}{1.3}

\newcommand{\eps}{\epsilon}
\newcommand{\fl}{\text{fl}}
\newcommand{\Lp}{{L^p}}
\newcommand{\Ker}{\text{Ker}\,}
\newcommand{\loc}{{\text{loc}}}
\newcommand{\ccinf}{C_c^\infty}
\newcommand{\supp}{\text{supp}}
\newcommand{\dist}{\text{dist}}

% Gravitational acceleration
\newcommand{\bg}{\mathbf{g}}
% Friction force
\newcommand{\bFf}{\mathbf{F_f}}
% Gravitational force
\newcommand{\bFg}{\mathbf{F_g}}
% Force
\newcommand{\bF}{\mathbf{F}}
% Position, velocity, acceleration
\newcommand{\br}{\mathbf{r}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\ba}{\mathbf{a}}

% Jacobian
\newcommand{\bDF}{\mathbf{DF}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\title{Checklist for Assignment 1}
\date{\vspace{-5em}}
\begin{document}
\maketitle
\section{Basics}

\begin{enumerate}
\item Is the front page as specified?
\item Is there a table of contents?
\item Does every section/subsection have a meaningful title?
\item Are there any references which are broken?
\item Is there anything missing: figures, tables, codes?
\item Does every figure and table have a meaningful caption?
\item Does every figure have meaningful labels?
\item Does the report contain the entire source code?
\item Is the source code {\tt MATLAB} compatible?
\item Does the source code adhere to the class standard? Specifically:
  \begin{enumerate}
  \item Does every function have a meaningful name and a short description
  \item Complete call sequence
  \item Complete input and output description
  \item Named minimal working example
  \item Author name(s) and contact info
  \item A brief revision history
  \item Inline comments provide good explanation of every nontrivial step
  \end{enumerate}
\end{enumerate}

\section{Intermediate}

\begin{enumerate}
\item Is there an introduction which explains the purpose of the report?
\item Can the report be read and understood by somebody who has not read the specification?
\item Is it easy to locate the answer to each question?
\end{enumerate}

\section{Advanced}

\begin{enumerate}
\item Is it clear to the reader why we so carefully collect information about the polynomials $T_n$?
\item Does the report distinguish clearly between the residual, i.e., the computed value of $y = T_n(x)$ and the error $r-x$, where $r$ is the relevant root?
\item Is is clearly explained why maintaining a bracket around a root is crucial when computing the relative error?
\item Is it clearly explained when and why the exact value of $y=T_n(x)$ has the same sign as the computed value $\hat{y}$?
\item Is there a conclusion summarizing the lessons learned during the production of the report?
\end{enumerate}

\end{document}


