\documentclass[a4paper,12pt]{article}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry} 
\usepackage{amsmath,amssymb,amsthm,algorithm,algorithmic,graphicx,yhmath,url,enumitem,lscape,hyperref}
\usepackage{wrapfig,subfigure}
\usepackage{lineno}

\newcounter{problem}
\newcounter{remark}
\newcounter{hint}
\newenvironment{remark}{\refstepcounter{remark} \vspace{0.1cm} \par \noindent {\bf Remark \arabic{remark}}}{\vspace{0.3cm}}
\newenvironment{hint}{\refstepcounter{hint} \vspace{0.1cm} \par \noindent {\bf Hint \arabic{hint}}}{\vspace{0.3cm}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Rn}{\mathbb{R}^n}
\newcommand{\Rnn}{\mathbb{R}^{n \times n}}
\newcommand{\bes}{\begin{equation*}}
\newcommand{\ees}{\end{equation*}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bms}{\begin{multline*}}
\newcommand{\emults}{\end{multline*}}

% Matrices
\newcommand{\bbm}{\begin{bmatrix}}
\newcommand{\ebm}{\end{bmatrix}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}

% Strecthing
\renewcommand{\arraystretch}{1.3}

\newcommand{\eps}{\epsilon}
\newcommand{\fl}{\text{fl}}
\newcommand{\Lp}{{L^p}}
\newcommand{\Ker}{\text{Ker}\,}
\newcommand{\loc}{{\text{loc}}}
\newcommand{\ccinf}{C_c^\infty}
\newcommand{\supp}{\text{supp}}
\newcommand{\dist}{\text{dist}}

% Gravitational acceleration
\newcommand{\bg}{\mathbf{g}}
% Friction force
\newcommand{\bFf}{\mathbf{F_f}}
% Gravitational force
\newcommand{\bFg}{\mathbf{F_g}}
% Force
\newcommand{\bF}{\mathbf{F}}
% Position, velocity, acceleration
\newcommand{\br}{\mathbf{r}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\ba}{\mathbf{a}}

% Jacobian
\newcommand{\bDF}{\mathbf{DF}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\title{Checklist for Assignment 2}
\date{\vspace{-5em}}
\begin{document}
\maketitle
\section{Basics}

\begin{enumerate}
\item Is the front page as specified?
\item Is there a table of contents?
\item Does every section/subsection have a meaningful title?
\item Are there any references which are broken?
\item Is there anything missing: figures, tables, codes?
\item Does every figure and table have a meaningful caption?
\item Does every figure have meaningful labels?
\item Does the report contain the entire source code?
\item Is the source code {\tt MATLAB} compatible?
\item Does the source code adhere to the class standard? Specifically:
  \begin{enumerate}
  \item Does every function have a meaningful name and a short description
  \item Complete call sequence
  \item Complete input and output description
  \item Named minimal working example
  \item Author name(s) and contact info
  \item A brief revision history
  \item Inline comments provide good explanation of every nontrivial step
  \end{enumerate}
\end{enumerate}

\section{Intermediate}

\begin{enumerate}
\item Is there an introduction which explains the purpose of the report?
\item Can the report be read and understood by somebody who has not read the specification?
\item Is it easy to locate the answer to each question?
\end{enumerate}

\section{Advanced}

\begin{enumerate}
\item Is relationship between the order of method and the slope of certain straight lines clearly explained?

\item Is it clearly explained why all relevant functions are differentiable. In particular, does the text include the appropriate references to the chain rule of differentiation?
  
\item Is it clearly documented how we construct Hermite's approximation for a function $f$ on a large interval?

\item Is there a conclusion which lists the lessons learned and as well as any unresolved issues?

\item Is the clear to the reader that computed time to impact with the hill is only an approximation, not the true value of time to impact?
\end{enumerate}

\end{document}


